\pkg{cleanR}: Maid for Cleaning Datasets in \proglang{R}

### 2016-12-30 latex/article_vol2.tex
Fixed appendix

\hl{Alle pakker. Andet?}

\appendix

\section{Appendix A: cleaning the toyData data frame} \label{sec:appendix1}
\includepdf[pages=2-4, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_toyData.pdf}

\section{Appendix B: User-extended cleaning of  testData} \label{sec:appendix2}
\includepdf[pages=2-, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_exampleData.pdf}
%\hl{Data cleaning with user supplied extensions here}

>>>>

\appendix
\newpage

%\includepdf[scale=0.8,clip,trim=0cm 0cm 0cm
%2cm,pages={1},pagecommand={\section{appendix}\subsection{par‌​t1}}]{pdfdocument} \includepdf[sc%ale=0.8,clip,trim=0cm
%0cm 0cm 2cm,pages={2-5},pagecommand={}]{pdfdocument}

% \section{Appendix A: cleaning the toyData data frame} \label{sec:appendix1}
\includepdf[pages=2, pagecommand={\section{Appendix A: cleaning the toyData data frame} \label{sec:appendix1}}, frame=true, noautoscale=true, scale=0.7]{cleanR_toyData.pdf}
\includepdf[pages=3-4, pagecommand={}, frame=true, noautoscale=true, scale=0.7,pagecommand={}]{cleanR_toyData.pdf}

\includepdf[pages=2, pagecommand={\section{Appendix B: User-extended cleaning of
  exampleData} \label{sec:appendix2}}, frame=true, noautoscale=true, scale=0.7]{cleanR_toyData.pdf}
\includepdf[pages=3-, pagecommand={}, frame=true, noautoscale=true, scale=0.7]{cleanR_exampleData.pdf}
%\hl{Data cleaning with user supplied extensions here}
